RationalGRL: A Framework for Argumentation and Goal Modeling

### 2017-08-15 formalframework.tex
Some minor changes
Previous version didn’t compile

We assume familiarity with basic notions from propositonal logic and set theory. A \emph{propositional atom} is a grounded formula (a formula without variables) with no logical connectives ($\vee, \and, \rightarrow, \leftrightarrow$) or negation ($\not$). We use integers $i,j\in\mathbb{N}$ as identifiers for actors and GRL elements.

>>>>

We assume familiarity with basic notions from propositonal logic and set theory. A \emph{propositional atom} is a grounded formula (a formula without variables) with no logical connectives ($\vee, \wedge, \rightarrow, \leftrightarrow$) or negation ($\neg$). We use integers $i,j,k\in\mathbb{N}$ as identifiers for actors and GRL elements.
